Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries

### 2024-05-01 paper.qmd
working references and keywords in abstract

---
title: "Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries"
author: "Vincent Xie"
toc: false
number-sections: false
execute:
    echo: false
highlight-style: pygments
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: 
    fontsize: 12pt
    geometry: 
      - top=30mm
      - left=20mm
header-includes:
  - \usepackage{setspace}
  - \doublespacing
##  docx: default
---
```{python}
# Packages
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import statsmodels.api as sm
from scipy.stats import chi2_contingency
import numpy as np
import warnings

@@

@@

Prior research in sports medicine and athletic injuries has primarily focused on immediate causes and rehabilitation of injuries. Within the NFL, the annual health and safety reports provide aggregate data on injury types and frequencies, which serve as a baseline for this study. However, there is a lack of comprehensive analysis that integrates environmental conditions, play strategies, and player-specific variables to predict and analyze injury occurrences comprehensively. There is also research on how the surface type affects the frequency in lower extremity injuries. The results show a positive correlation between the two factors. This paper will also perform statistical analysis on how specific factors affect the frequency of lower extremity injuries. It may support the claims of prior research or provide new insight on other causes that may contribute to these injuries.

@@

This paper contributes to the existing literature by employing statistical techniques to analyze a unique dataset combining player injury records, play-by-play data, and environmental conditions. By doing so, it aims to:

@@

# Websites for reference

+ https://pubmed.ncbi.nlm.nih.gov/30452873/
+ https://pubmed.ncbi.nlm.nih.gov/30697503/
+ https://journals.sagepub.com/doi/pdf/10.1177/0363546518808499

>>>>

---
title: "Decoding the Impact: Statistical Analysis of Factors Contributing to NFL Injuries"
author: "Vincent Xie"
bibliography: references.bib
toc: false
number-sections: false
execute:
    echo: false
highlight-style: pygments
format: 
  html: 
    code-fold: true
    html-math-method: katex
  pdf: 
    fontsize: 12pt
    geometry: 
      - top=30mm
      - left=20mm
header-includes:
  - \usepackage{setspace}
  - \doublespacing
##  docx: default
---
```{python}
# Packages
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import statsmodels.api as sm
from scipy.stats import chi2_contingency
import numpy as np
import warnings

@@

**Keywords**: environmental factors; lower extremity; natural turf; NFL injuries; stadium surface; synthetic turf

@@

Prior research in sports medicine and athletic injuries has primarily focused on immediate causes and rehabilitation of injuries. Within the NFL, the annual health and safety reports provide aggregate data on injury types and frequencies, which serve as a baseline for this study. However, there is a lack of comprehensive analysis that integrates environmental conditions, play strategies, and player-specific variables to predict and analyze injury occurrences comprehensively. There is also research on how the surface type affects the frequency in lower extremity injuries. The results from @Mack2018 show a positive correlation between the two factors. Notably, there was a 16% increase in lower extremity injuries on synthetic fields. @Haider2018 did another study on concussions and how it was affected by environmental factors. Although not related to this paper, it highlights the idea that environmental factors such as temperature and weather are impactful in regards to injuries.

@@

This paper contributes to the existing literature by employing statistical techniques to analyze a unique dataset combining player injury records, play-by-play data, and environmental conditions. By examining the frequency of lower extremity injuries, it may support the claims of prior research. By doing so, it aims to:

@@

# References
